---
title: Plot wordcloud graph using quanteda R package
author: Jinshuai Ma
date: '2020-08-07'
slug: plot-wordcloud-graph-using-quanteda-r-package
categories:
  - R
tags:
  - quanteda
Description: ''
Tags: []
Categories: []
DisableComments: no
---

Quanteda is an R package for managing and analyzing text (https://quanteda.io/). One benefit of using quanteda is its powerful plot tools. You can easily plot a wordcloud graph for a set of documents, i.e. a corpus.

Here, we will use quanteda's build-in corpus, the *inaugural address corpus* to demonstrate how to plot a wordcloud graph.

**Step 1:** load quanteda package.

```{r message=FALSE}
library("quanteda")
```

**Step 2:** create a dfm (Document features matrix) by tokenize the corpus.

```{r}
my_tokens = tokens(data_corpus_inaugural, remove_punct = TRUE, remove_symbols = TRUE)
my_dfm = dfm(my_tokens, remove=stopwords(language = "en"))
```

**Step 3:** we use that dfm to plot a wordcloud graph.

```{r}
textplot_wordcloud(my_dfm, max_words=200)

```

There many more options for the plot. Please refer to [textplot_wordcloud](https://quanteda.io/reference/textplot_wordcloud.html) for more details.